### 2014-03-17 Draft/abstract.tex
Dr. Xie's coments

\begin{abstract}
Temporal constraints of an Application Programming
Interface (API) are the allowed sequences of invocations
of methods from the API.
These constraints govern the secure and robust
operation of client software using the API.
Typically, these constraints are described in natural language text
of API documents and thus cannot be used by existing verification tools
which typically accept only formal constraints.
Because manually writing temporal constraints based on
API documents can be prohibitively time consuming and error prone,
we propose \tool: a Natural Language Processing (NLP) based approach
to automatically infer temporal constraints.
In particular, our approach includes novel techniques to reduce the number of lexical tokens
as a way to make API documents amenable to existing NLP techniques
(that are currently designed to work on well written news articles).
Our approach also includes a novel technique of identifying method references in
the natural language text by building domain-dictionaries systematically
from API documents and generic English dictionaries.
To evaluate our approach, we apply \tool\ to infer temporal constraints from 
commonly used package \CodeIn{java.io} in the JDK API and from the \amazonAPI.
Our results show that \tool\ effectively identifies constraint sentences (from over 3900 API sentences) with the average precision, recall, and F-score of 65.0\%, 72.2\%, and 68.4\%, respectively.
Furthermore, \tool\ also achieves an accuracy of 70\% in inferring 63 temporal constraints from these sentences.

>>>>

\begin{abstract}
Temporal constraints of an Application Programming
Interface (API) are the allowed sequences of invocations
of methods from the API.
These constraints govern the secure and robust
operation of client software using the API.
Typically, these constraints are described in natural language text
of API documents and thus cannot be used by existing verification tools,
which typically accept only formal constraints.
Because manually writing temporal constraints based on
API documents can be prohibitively time consuming and error prone,
we propose \tool: a Natural Language Processing (NLP) based approach
to automatically infer temporal constraints.
In particular, our approach includes a novel technique to reduce the number of lexical tokens
as a way to make API documents amenable to existing NLP techniques
(which are typically designed to work on well-written news articles).
Our approach also includes a novel technique of identifying method references in
the natural language text by building domain dictionaries systematically
from API documents and generic English dictionaries.
To evaluate our approach, we apply \tool\ to infer temporal constraints from 
commonly used package \CodeIn{java.io} in the JDK API and from the \amazonAPI.
Our results show that \tool\ effectively identifies constraint sentences (from over 3900 API sentences) with the average precision, recall, and F-score of 65.0\%, 72.2\%, and 68.4\%, respectively.
Furthermore, \tool\ also achieves an accuracy of 70\% in inferring 63 temporal constraints from these sentences.

### 2014-03-17 Draft/approach.tex
Dr. Xie's coments

The preprocessor accepts the API documents and extracts method descriptions from it.
In particular, the preprocessor extracts the following fields within method descriptions: 
1) \textit{Summary of the API method},
2) \textit{Summary and type information of parameters of the API method}, 
3) \textit{Summary and type information of return values of the method}, and
4) \textit{Summary and type information of exceptions thrown by the methods}.

@@

The NLP parser accepts the pre-processed documents and annotates every sentence within each document using core NLP techniques described in Section~\ref{sub:CoreNLPback}.
From an implementation perspective, we chose the Stanford parser~\cite{Manning:01}.
However, this component can be implemented using any other existing NLP libraries or approaches.
In particular, we annotate each sentence with POS tags, named-entity annotations and Stanford-typed dependencies.
For more details on these techniques and their application, please refer to ~\cite{Marneffe06LREC, Marneffe08COLING, pandita12:inferring, pandita13:WHYPER, thummalapentaICSE12}.

@@

Our algorithm systematically explores the FOL representation
of the candidate sentence to determine if a sentence
describes a temporal constraint. First, our algorithm
attempts to locate the occurrence of class name or its synonym
within the leaf nodes of the FOL
representation of the sentence (Line 3). The method
findLeafContaining(r\_name\_list) explores the FOL representation
to find a leaf node that contains either the class name
or one of its synonyms.
In particular, we use WordNet~\cite{wordnet} and Lemmatisation
to deal with synonyms of a word in question to find appropriate
matches. Once a leaf node is found, we systematically
traverse the tree from the leaf node to the root,
matching all parent predicates as well as immediate child
predicates [Lines 5-16].

@@

A key way of identifying reference to a method within the API in our proposed approach is the employment of a semantic graph of an API.
In particular, we propose to initially infer such graphs from API documents.
Manually creating a semantic graph is prohibitively time consuming and may be error prone.
We thus employ a systematic methodology (proposed previously in ~\cite{pandita13:WHYPER}) to infer such semantic graphs from API documents that can potentially be automated.
We first consider the name of the class for the API document in question.
We then find the synonyms terms used refer to the class in question.
The synonym terms are listed as by breaking down the camel-case notation in the class name.
This list is further augmented by listing the name of the parent classes and implemented interfaces if any.

>>>>

The preprocessor accepts the API documents and extracts method descriptions from it.
In particular, the preprocessor extracts the following fields from the method descriptions: 
1) \textit{Summary of the API method},
2) \textit{Summary and type information of parameters of the API method}, 
3) \textit{Summary and type information of return values of the method}, and
4) \textit{Summary and type information of exceptions thrown by the methods}.

@@

The NLP parser accepts the pre-processed documents and annotates every sentence in each document using core NLP techniques described in Section~\ref{sub:CoreNLPback}.
From an implementation perspective, we chose the Stanford parser~\cite{Manning:01}.
However, this component can be implemented using any other existing NLP libraries or approaches.
In particular, we annotate each sentence with POS tags, named-entity annotations and Stanford-typed dependencies.
For more details on these techniques and their application, please refer to ~\cite{Marneffe06LREC, Marneffe08COLING, pandita12:inferring, pandita13:WHYPER, thummalapentaICSE12}.

@@

Our algorithm systematically explores the FOL representation
of the candidate sentence to determine if a sentence
describes a temporal constraint. First, our algorithm
attempts to locate the occurrence of class name or its synonym
in the leaf nodes of the FOL
representation of the sentence (Line 3). The method
findLeafContaining(r\_name\_list) explores the FOL representation
to find a leaf node that contains either the class name
or one of its synonyms.
In particular, we use WordNet~\cite{wordnet} and Lemmatisation
to deal with synonyms of a word in question to find appropriate
matches. Once a leaf node is found, we systematically
traverse the tree from the leaf node to the root,
matching all parent predicates as well as immediate child
predicates [Lines 5-16].

@@

A key way of identifying reference to a method in the API by our approach is the employment of a semantic graph of an API.
In particular, we propose to initially infer such graphs from API documents.
Manually creating a semantic graph is prohibitively time consuming and may be error prone.
We thus employ a systematic methodology (proposed previously in ~\cite{pandita13:WHYPER}) to infer such semantic graphs from API documents that can potentially be automated.
We first consider the name of the class for the API document in question.
We then find the synonyms terms used refer to the class in question.
The synonym terms are listed as by breaking down the camel-case notation in the class name.
This list is further augmented by listing the name of the parent classes and implemented interfaces if any.

### 2014-03-17 Draft/conclusion.tex
Dr. Xie's coments

Although highly desirable, most API's do not have formal temporal constraints.
In contrast, documentation of methods contain detailed specifications of the usage in natural language text.
Manually writing formal specifications based on natural language text in API documents is prohibitively time consuming and error prone.
To address this issue, we proposed a novel approach \tool\ to infer temporal constraints from natural language text of API documents.
We applied \tool\ to infer temporal constraints from 
commonly used package \CodeIn{java.io} in the JDK API and from the Amazon S3 REST API.
Our evaluation results show that \tool\ effectively identifies sentences describing
temporal constraints with an average 65\% precision and 72\% recall,
from more than 3900 sentences in subject API documents.
Furthermore,\tool\ also achieved an  accuracy of
70\% in inferring 63 formal temporal constraints from these sentences.

>>>>

Despite being highly desirable, most APIs are not equipped with formal temporal constraints.
In contrast, documentation of API methods contains detailed specifications of temporal constraints in natural language text.
Manually writing formal specifications based on natural language text in API documents is prohibitively time consuming and error prone.
To address this issue, we have proposed a novel approach called \tool\ to infer temporal constraints from natural language text of API documents.
We applied \tool\ to infer temporal constraints from 
commonly used package \CodeIn{java.io} in the JDK API and from the \amazonAPI.
Our evaluation results show that \tool\ effectively identifies sentences describing
temporal constraints with an average 65\% precision and 72\% recall,
from more than 3900 sentences in subject API documents.
Furthermore, \tool\ also achieved an accuracy of
70\% in inferring 63 formal temporal constraints from these sentences.

### 2014-03-17 Draft/introduction.tex
Dr. Xie's coments

Temporal constraints~\cite{ball2002s} of an Application Programming Interface (API) 
are the allowed sequences of invocations of methods within the API. 
These constraints govern the secure and robust operation of client software using the API.
If these constraints are formal (machine-readable such as linear temporal logic),
they can be used as inputs to the formal analysis tools such 
as model checker and runtime verifiers
in detecting the violations of these temporal constraints as defects~\cite{lee2012towards}.

Typically, these constraints are described in natural language text of API documents.
Such documents are provided to client-code developers through an online access, or are shipped with the API code.
For a method under consideration, an API document may describe both the constraints on that method parameters
as well as the temporal constraints in terms of methods that must be invoked pre/post that method.
We observed that an considerable portion (roughly 12\%) of the sentences (that describe some sort of constraints)
in \amazonAPI\ documentations describe temporal constraints.
However, existing verification tools which typically accept only formal constraints
cannot use the natural language constraints from API documents.

One way of addressing the issue, is to manually convert the natural language API description into formal constraints. 
However, manually writing formal constraints based on natural language text in API documents can be prohibitively time consuming and error prone~\cite{wu2013inferring,RubingerWEB10}. 
For instance, Wu et al.~\cite{wu2013inferring} report that it took one of the authors hours to browse the documentation of one method of a web service API, even before they attempted to formalize the constraints on the method.
To reduce the manual effort, we propose \tool: a Natural Language Processing (NLP) based approach
to automatically infer formal temporal constraints. 
%Strike out ``To address the aforementioned issue''
%We propose a novel approach to infer temporal usage constraints from natural language text of API documents.

%In particular, we focus on specific type of constraints namely temporal constraints.
%A generic temporal constraint is defined as \textit{an interpropositional constraint that communicates the ordering in time of events or states.}
%In terms of API method constraints, we interpret temporal constraints as \textit{`the allowed sequence of invocations of methods'}.
%For example, consider the following statement in \amazonAPI\ ``You must initiate a multipart upload before you can upload any part.''
%We can interpret this sentence stating that a multipart-upload method must be invoked before invoking any part-upload method in the API.

%Move this paragraph to later sections or may be push later in intro
% make example flow in next paragraph
% Make consistent terminology approach or technique

%Background on out of how many sentences

% Combine first two sentences
% In contrast, temporal constraints are beyond these parameter constraints. may be use difficult to express using parameter constraints
% Amazon S3 is popularly used web service for simple cloud based storage
Although, existing approaches focus on inferring method pre-post conditions (in terms of parameter constraints) using either program analysis techniques~\cite{Henkel07discoveringdocumentation,Ghezzi:2009:SIB:1555001.1555057,Henkel:2008:DDA:1363102.1363105,Flanagan2001:HAA,Buse:2008:ADI:1390630.1390664} or NLP~\cite{pandita12:inferring, wu2013inferring}, temporal constraints are beyond these parameter constraints.
Temporal constraints, in general focus on rules related to orchestration of methods within an API rather than focusing on the requirements on the input parameters of these methods.

Apart from method specifications, Zhong et al.~\cite{zhong09SE} leverage machine learning and type information to infer constraints on resources based on phases of resource usage: creating, manipulating, and releasing. However, temporal constraints are not limited to resource usage. Furthermore, their approach fails to make the finer grained distinction on the ordering of the methods within a phase. For the description mentioned in previously, assuming that the method calls are associated with resource ``part'', both the methods referenced are logically associated with the creation phase of resource. Zhong et al.~\cite{zhong09SE} approach fails to make a distinction in ordering of such methods. In contrast our proposed approach leverages natural language processing to infer generic temporal constraints (not limited to resource related constraints) and also improves upon existing work for making finer grained distinction between ordering of methods within a phase of a resource.

%First, relying just on type information will result in an incomplete list of temporal constraints. 
%In typed languages some temporal constraints are enforced by type system. 
%For instances a method ($m$) accepting input parameter ($i$) of type ($t$) mandates that (at least one) method ($m'$) be invoked whose return value is of type ($t$).
%However, temporal constraints are not limited by the type definitions (i.e, requirements on the type of input parameters), and are currently expressed mostly in natural language in API documents, as described in the example previously.
%We propose to address the issue by augmenting the type definitions based temporal constraints with the constraints inferred from
%the natural language text in API documents.
%Furthermore, such constraints although valuable but are already checked by any advanced Integrated Development Environment(IDE) such as eclipse
%for a strongly typed language.
%The problem is exacerbated in web based API's such as \amazonAPI\ where most of the types are either \CodeIn{integer} or \CodeIn{strings}.
%Our proposed approach extends the existing approaches to address the challenge.

%identified in previous work~\cite{pandita12:inferring} delete and leave the reference
% Add a sentence stating that we extend previous technique to address the issues 
However, inferring temporal constraints from the natural language text is challenging. 
There are existing challenges in NLP for software engineering domain namely \textit{ambiguity}, \textit{programming keywords}, and \textit{semantic equivalence} identified in previous work~\cite{pandita12:inferring}.
In addition to these challenges, we have an added challenge of 
implicit method referencing: identifying the method referenced in the natural language text to infer temporal constraint.
Recall the description sentence ``You must initiate a multipart upload before you can upload any part.''
In this sentence, phrases ``multipart upload'' and ``upload any part'' refer to individual methods in the API.
Identifying these phrases as method invocation instances requires domain dictionaries.
Ad-hoc construction of such dictionaries is prohibitively time and resources intensive.
To address this challenge, we propose to build domain-dictionaries systematically from API documents and generic English dictionaries.

% talk about mining approaches 
In summary, the proposed work leverages natural language description of API's to infer temporal constraints of method invocations.
As the proposed work analyzes API documents in natural language, it can be reused independent of the programming language of the API library.
Additionally, our approach complements existing mining based approaches~\cite{buse2012synthesizing, thummalapenta07parseweb, Wang:2013:MSR, Zhong:2009:MMR} that partially address the problem by mining for common usage patterns among client software that use the API.
The proposed work in general, makes the following contributions:
%However, all of these approaches rely on the availability of the source code that use API methods under investigation.
%Furthermore, these approaches are limited by both the quantity as well as quality of data set (source code) available.
%To address the limitation we propose to extend the natural language infrastructure developed previously~\cite{pandita12:inferring,pandita2013whyper} to focus specifically on the temporal constraints.

%Use consistent term technique or approach
%Methodology for generating domain dictionaries 
\begin{itemize}
	\item An NLP based approach that infers temporal constraints of method invocations. 
	To the best of our knowledge, our approach is the first one to apply NLP for the goal of inferring temporal constraints from API documents.
	\item A prototype implementation of our approach based on extending the Stanford Parser~\cite{Klein03}, which is a natural language parser to derive the grammatical structure of sentences.
	An open source implementation of the prototype is publicly available on our project website\footnote{\url{https://sites.google.com/site/temporalspec}}. 
	\item An evaluation of proposed approach on commonly used package \CodeIn{java.io} from JDK API and \amazonAPI. 
\end{itemize}

The rest of the paper is organized as follows.
Section~\ref{sec:example} presents real world examples that motivate our approach.
Section~\ref{sec:related} discusses related work in this area.
Section~\ref{sec:background} presents the  background on NLP techniques used in this work.
Section~\ref{sec:approach} presents our approach.
Section~\ref{sec:evaluation} presents evaluation of our approach.
Section~\ref{sec:discussion} presents a brief discussion and future work.
Finally, Section~\ref{sec:conclusion} concludes.

% how well does the NLP based technique augument the type based temporal constraints

>>>>

Temporal constraints~\cite{ball2002s} of an Application Programming Interface (API) 
are the allowed sequences of invocations of methods from the API. 
These constraints govern the secure and robust operation of client software using the API.
If these constraints are in a formal specification language,
they can be used as inputs to formal analysis tools such 
as model checker and runtime verifiers
in detecting the violations of these temporal constraints as defects~\cite{lee2012towards}.

Typically, temporal constraints are described in natural language text of API documents.
Such documents are provided to client-code developers through an online access, or are shipped with the API code.
For a method under consideration, an API document may describe both the constraints on the method parameters
as well as the temporal constraints in terms of other methods that must be invoked pre/post invoking that method.
We observe that a non-trivial portion (roughly 12\%) of the sentences (constraint-describing sentences)
in \amazonAPI\ documentation describe temporal constraints.
However, existing verification tools, which typically accept only formal constraints,
cannot use the natural language constraints from API documents.

Although natural language API description can be manually converted into formal constraints,
manually writing formal constraints based on natural language text in API documents can be prohibitively time consuming and error prone~\cite{wu2013inferring,RubingerWEB10}. 
For instance, Wu et al.~\cite{wu2013inferring} report that it took one person ten hours to browse the documentation of one method from a web service API, even before the person attempted to formalize the constraints on the method.

To reduce the manual effort, we propose \tool: a Natural Language Processing (NLP) based approach
to automatically infer formal temporal constraints. 
However, inferring temporal constraints from the natural language text is challenging. 
In particular, our approach addresses two major challenges to automatically infer specifications
from natural language text in API documents.

First, existing NLP techniques are initially designed towards well-written news articles.
In contrast, API documents are domain-specific documents and are often not well formed.
Furthermore, we observe that generic NLP techniques face problems with lengthy sentences (with a number of lexical tokens).
Consider the description sentence ``All objects (including all object versions and Delete Markers) in the bucket must be deleted before the bucket itself can be delete.'' The length of the sentence may overwhelm an NLP parser, which then inaccurately extracts semantic relations between the words in the sentence.
Our ICON approach includes a new technique called ``hybrid parsing'' to deal with the number of lexical tokens.
Hybrid parsing automatically breaks lengthy sentences to smaller tractable sentences based on a function of parts-of-speech tags.

Second, after API documents are made amenable to existing NLP techniques, a method referenced in the natural language text must be identified in order to infer temporal constraints on the method but such method referencing is often implicit.
Consider the description sentence ``You must initiate a multipart upload before you can upload any part.''
In this sentence, phrases ``multipart upload'' and ``upload any part'' refer to individual methods in the API.
Identifying these phrases as method-invocation instances requires domain dictionaries.
Ad-hoc construction of such dictionaries is prohibitively time and resource intensive.
To address this challenge, we propose to build domain dictionaries systematically from API documents and generic English dictionaries.

In summary, our \tool\ approach leverages natural language description of API's to infer temporal constraints of method invocations.
As our approach analyzes API documents in natural language, it can be reused independent of the programming language of an API library.
Additionally, our approach complements existing mining-based approaches~\cite{buse2012synthesizing, thummalapenta07parseweb, Wang:2013:MSR, Zhong:2009:MMR} that partially address the problem by mining for common usage patterns among client code reusing the API.
This paper makes the following main contributions:
%However, all of these approaches rely on the availability of the source code that use API methods under investigation. Furthermore, these approaches are limited by both the quantity as well as quality of data set (source code) available. To address the limitation we propose to extend the natural language infrastructure developed previously~\cite{pandita12:inferring,pandita2013whyper} to focus specifically on the temporal constraints.

\begin{itemize}
	\item An NLP-based approach that effectively infers temporal constraints of method invocations. 
	To the best of our knowledge, our approach is the first one to apply NLP for inferring temporal constraints from API documents.
	\item A prototype implementation of our approach based on extending the Stanford Parser~\cite{Klein03}, which is a natural language parser to derive the grammatical structure of sentences.
	An open source implementation of the prototype is publicly available on our project website\footnote{\url{https://sites.google.com/site/temporalspec}}, along with the experimental subjects and the results. 
	\item An evaluation of our approach on commonly used package \CodeIn{java.io} from the JDK API and from \amazonAPI. 
\end{itemize}

The rest of the paper is organized as follows.
Section~\ref{sec:example} presents a real-world example that motivates our approach.
Section~\ref{sec:related} discusses related work.
Section~\ref{sec:background} presents the  background on NLP techniques used in our approach.
Section~\ref{sec:approach} presents our approach.
Section~\ref{sec:evaluation} presents the evaluation of our approach.
Section~\ref{sec:discussion} presents brief discussion and future work.
Finally, Section~\ref{sec:conclusion} concludes.

%In particular, we focus on specific type of constraints namely temporal constraints. A generic temporal constraint is defined as \textit{an interpropositional constraint that communicates the ordering in time of events or states.} In terms of API method constraints, we interpret temporal constraints as \textit{`the allowed sequence of invocations of methods'}. For example, consider the following statement in \amazonAPI\ ``You must initiate a multipart upload before you can upload any part.'' We can interpret this sentence stating that a multipart-upload method must be invoked before invoking any part-upload method in the API.

%Although, existing approaches focus on inferring method pre-post conditions (in terms of parameter constraints) using either program analysis techniques~\cite{Henkel07discoveringdocumentation,Ghezzi:2009:SIB:1555001.1555057,Henkel:2008:DDA:1363102.1363105,Flanagan2001:HAA,Buse:2008:ADI:1390630.1390664} or NLP~\cite{pandita12:inferring, wu2013inferring}, temporal constraints are beyond these parameter constraints. Temporal constraints, in general focus on rules related to orchestration of methods within an API rather than focusing on the requirements on the input parameters of these methods.

%Apart from method specifications, Zhong et al.~\cite{zhong09SE} leverage machine learning and type information to infer constraints on resources based on phases of resource usage: creating, manipulating, and releasing. However, temporal constraints are not limited to resource usage. Furthermore, their approach fails to make the finer grained distinction on the ordering of the methods within a phase. For the description mentioned in previously, assuming that the method calls are associated with resource ``part'', both the methods referenced are logically associated with the creation phase of resource. Zhong et al.~\cite{zhong09SE} approach fails to make a distinction in ordering of such methods. In contrast our proposed approach leverages natural language processing to infer generic temporal constraints (not limited to resource related constraints) and also improves upon existing work for making finer grained distinction between ordering of methods within a phase of a resource.

%First, relying just on type information will result in an incomplete list of temporal constraints. In typed languages some temporal constraints are enforced by type system. For instances a method ($m$) accepting input parameter ($i$) of type ($t$) mandates that (at least one) method ($m'$) be invoked whose return value is of type ($t$). However, temporal constraints are not limited by the type definitions (i.e, requirements on the type of input parameters), and are currently expressed mostly in natural language in API documents, as described in the example previously. We propose to address the issue by augmenting the type definitions based temporal constraints with the constraints inferred from the natural language text in API documents. Furthermore, such constraints although valuable but are already checked by any advanced Integrated Development Environment(IDE) such as eclipse for a strongly typed language. The problem is exacerbated in web based API's such as \amazonAPI\ where most of the types are either \CodeIn{integer} or \CodeIn{strings}. Our proposed approach extends the existing approaches to address the challenge.

### 2014-03-17 Draft/related.tex
Dr. Xie's coments

Our proposed approach touches a few research areas such as software verification, NLP in Software Engineering (SE), and document augmentation.
We next discuss the relevant work pertinent to our proposed approach in these areas.

@@

Zhong et al.~\cite{zhong09SE} leverage machine learning and type information to infer constraints on resources based on phases of resource usage: creating, manipulating, and releasing.
However, temporal constraints are not limited to resource usage thus 
Furthermore, the specifications inferred by their approach infers implicit specifications across multiple method descriptions,
whereas the temporal constraints inferred by our approach infers explicit ordering information described in individual method descriptions.
Furthermore, the performance of their approach is dependent on the quality of the training sets used for ML.
In contrast, approach presented in this report is independent of such training set and thus can be easily extended to target respective problems addressed by them.

Xiao et al.~\cite{XiaoFSE2012} and Slankas et al.~\cite{johnSlankasPASSAT13} use shallow parsing techniques to infer Access Control Policy (ACP) rules from natural language text in use cases.
The use of shallow parsing techniques works satisfactorily on natural language texts in use cases, owing to well-formed structure of sentences in use case descriptions.
In contrast, often the sentences in API documents are not well-formed.
Additionally, their approaches do not deal with programming keywords or identifiers, which are often mixed within the method descriptions in API documents.

Most closely related work to the approach presented here is our previous work on inferring parameter constraints from method descriptions in the API documents~\cite{pandita12:inferring}.
Our proposed approach differs from the previous approach as follows.
Our proposed approach addresses the problem of inferring temporal constraint, whereas the previous approach infers parameter constraints.
Our proposed approach is a significant extension to the infrastructure used in the previous work in following areas.
First, the proposed approach introduces hybrid shallow parsing that relies both on parts-of-speech tags as well as Stanford-typed dependencies to construct intermediate representation.
Second, the proposed approach introduces a new heuristics namely frequent phrase reduction to deal with the domain specific and ill-formed sentences in API documents.
Finally, the proposed approach leverages the concept of semantic graphs constructed from class and method names in API to automatically infer the implicit method references in a sentence.

\textbf{Augmented Documentation}:
Improving the documentation related to a software API~\cite{Dekel2009,tan2011acomment} is another related field of research.
Dekel and Herbsleb~\cite{Dekel2009}, were the first to create a tool namely eMoose,
an Eclipse~\footnote{\url{http://www.eclipse.org/}} based plug-in that allowed developers to create directives
(way of marking the specification sentences) in the default API documentation.
These directives are highlighted whenever they are displayed in the Eclipse environment.
Lee et al.~\cite{lee2012towards} improved upon their work by providing a formalism to the directives proposed by Dekel et al.~\cite{Dekel2009},
thus allowing tool-based verification.
However, a developer has to manually annotate such directives.
In contrast, our proposed approach both identifies the sentences pertaining to temporal constraints and infers the temporal constraints automatically.

>>>>

%Our proposed approach touches a few research areas such as software verification, NLP in Software Engineering (SE), and document augmentation.
%We next discuss the relevant work pertinent to our proposed approach in these areas.

@@

Zhong et al.~\cite{zhong09SE} leverage machine learning and type information to infer constraints on resources.
Specifically, their approach infers resource constraints following template: resource creation methods followed by resource manipulation methods followed by resource release methods.
However, temporal constraints may not be limited to such as template. 
Furthermore, the performance of their approach is dependent on the quality of the training sets used for ML.
In contrast, approach presented in this report is independent of such training set and thus can be easily extended to target respective problems addressed by them. Furthermore, the specifications inferred by their approach may ignore the explicit ordering information described in individual method descriptions as inferred by our approach.

Xiao et al.~\cite{XiaoFSE2012} and Slankas et al.~\cite{johnSlankasPASSAT13} use shallow parsing techniques to infer Access Control Policy (ACP) rules from natural language text in use cases.
The use of shallow parsing techniques works satisfactorily on natural language texts in use cases, owing to well-formed structure of sentences in use case descriptions.
In contrast, often the sentences in API documents are not well-formed.
Additionally, their approaches do not deal with programming keywords or identifiers, which are often mixed with the method descriptions in API documents.

Most closely related work to the approach presented here is our previous work on inferring parameter constraints from method descriptions in the API documents~\cite{pandita12:inferring}.
\tool\ approach differs from the previous approach as follows.
\tool\ approach addresses the problem of inferring temporal constraint, whereas the previous approach infers parameter constraints.
\tool\ approach is a significant extension to the infrastructure used in the previous work in following areas.
First, \tool\ approach introduces hybrid shallow parsing that relies both on parts-of-speech tags as well as Stanford-typed dependencies to construct intermediate representation, while the previous approach relies only on parts-of-speech tags.
Second, the \tool\ approach introduces a new heuristics namely frequent phrase reduction to deal with the domain specific and ill-formed sentences in API documents.
Finally, the \tool\ approach leverages the concept of semantic graphs constructed from class and method names in API to automatically infer the implicit method references in a sentence. In contrast, previous approach relies on predefined lists.

\textbf{Augmented Documentation}:
Improving the documentation related to a software API~\cite{Dekel2009,tan2011acomment} is another related field of research.
Dekel and Herbsleb~\cite{Dekel2009}, were the first to create a tool namely eMoose,
an Eclipse~\footnote{\url{http://www.eclipse.org/}} based plug-in that allowed developers to create directives
(way of marking the specification sentences) in the default API documentation.
These directives are highlighted whenever they are displayed in the Eclipse environment.
Lee et al.~\cite{lee2012towards} improved upon their work by providing a formalism to the directives proposed by Dekel et al.~\cite{Dekel2009},
thus allowing tool-based verification.
However, a developer has to manually annotate such directives.
In contrast, our approach both identifies the sentences pertaining to temporal constraints and infers the temporal constraints automatically.
